Data preparation: Study 1

### 2021-09-02 processing/preparation_study1.Rmd

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

This is the preparation code of the data for Study 1: Measuring meritocracy with international secondary data. The prepared data is `data_s1.RData`

>>>>

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```
This is the preparation code of the data for Study 1: Measuring meritocracy with international secondary data. The prepared data is `data_s1.RData`
